\sysfull

### 2017-08-09 paper/coalescing.tex
pass over the coalescing section

\sys is able to dynamically merge real tasks to construct a bigger virtual task. This enables \sys to reduce the number of commits by $\frac{\text{VTS}-1}{\text{VTS}}$, where VTS is virtual task size. Furthermore, \sys tries to estimate the optimal virtual task size by relying on its recent execution history. The challenge in designing \sys's coalescing algorithm is in introducing as less overhead as possible and able to respond to the changes in the environment as quickly as possible.

>>>>

\sys dynamically {\em coalesces} consecutively executing tasks at run time.
When two tasks are coalesced, the first of the two tasks does not commit its
updates to protected memory locations when it reaches a \transition statement.
Instead, execution immediately continues from the beginning of the second of
the two tasks.  At the end of the second of the two coalesced tasks, \sys
commits the pages that were updated by either of the coalescing tasks.  The
purpose of coalescing is to better amortize the run time overhead of committing
updated pages when a task ends. If consecutive tasks access the same pages of
data, the pages accessed by both tasks only need to be committed only once for
the coalesced task rather than twice, one time for each of the tasks executed
individually.

\sys can coalesce an arbitrary number consecutive tasks.  As more tasks
coalesce, their collective commit overhead amortizes better, potentially
improving performance.  As more tasks coalesce, the amount of potentially {\em
wasted work} also increases. If power fails during a long sequence of coalesced
tasks the lack of an intervening commit requires execution to restart from the
{\em first} task in the sequence, failing to preserve the progress of any of
the tasks in the long sequence.
